---
title: "Introduction to Machine Learning Assignment"
author: "Michael Gonzalez"
date: "May 09, 2019"
output:
  
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)

binClass <- read.csv('binary-classifier-data.csv')
triClass <- read.csv('trinary-classifier-data.csv')

```

## A. Plot the data from each dataset using a scatter plot.

Scatter plot of the binary classifier data: 

```{r echo = FALSE}
ggplot(binClass, aes(x = x, y = y)) + geom_point()

```

Scatter plot of the trinary classifier data:

```{r echo = FALSE}
ggplot(triClass, aes(x = x, y = y)) + geom_point()

```

## B. Fit a k nearest neighbors model for each dataset for k=3, k=5, k=10, k=15, k=20, and k=25. Compute the accuracy of the resulting models for each value of k. Plot the results in a graph where the x-axis is the different values of k and the y-axis is the accuracy of the model.

Plot of the binary classifier data: 

```{r echo = FALSE}
binKvalues <- c(3, 5, 10, 15, 20, 25)
binPercents <- c(99, 97, 93, 90, 87, 87)
binDf <- data.frame(Kvalues = binKvalues, Percents = binPercents)

ggplot(binDf, aes(x = Kvalues, y = Percents)) +
  geom_line() +
  labs(title = "Accuracy Model of Binary Classifiers", x = "K Values", y = "Accuracy of Model (%)")
```


Plot of the trinary classifier data:

```{r echo = FALSE}
triKvalues <- c(3, 5, 10, 15, 20, 25)
triPercents <- c(97, 95, 90, 84, 81, 78)
triDf <- data.frame(Kvalues = triKvalues, Percents = triPercents)

ggplot(triDf, aes(x = Kvalues, y = Percents)) +
  geom_line() +
  labs(title = "Accuracy Model of Trinary Classifiers", x = "K Values", y = "Accuracy of Model (%)")
```


## C. Looking back at the plots of the data, do you think a linear classifier would work well on these datasets?

I do believe that linear classifier might give better results to see the data sets. Comparing these plots to the scatter plots, the data is clear for anyone to see the results.

